---
title: "Waste Pickers"
subtitle: "md-08-am-01"
date: today
author: Fionn Smith, haella003, FOFOS22
bibliography: waste-pickers.bib
format: revealjs
execute:
  warning: false
editor: visual
---

## Research Question

Formalization of Informal Waste Pickers’ Cooperatives in Blantyre, Malawi: A Feasibility Assessment\
@kasinja2018formalization \
<br> Could formalization of IWPs into cooperatives be effective and/or accepted as a way of managing Municipal Solid Waste in unplanned urban settlements in Malawi?

```{r}

```

## Sampling Strategy

-   On-site interviews of active IWP collecting in Zingwangwa, Malawi

-   Snowball strategy till saturation

```{r}

```

## Key Findings

Could formalization of IWPs into cooperatives be effective and/or accepted as a way of managing Municipal Solid Waste in unplanned urban settlements in Malawi?<br>\
With the right support it could potentially be effective at increasing bargaining power of IWPs, thus having the potential to limit exploitative pricing from buyers.

```{r}

```

## Sources

```{r}

```
