---
title: "Waste Pickers"
subtitle: "md-08-am-01"
date: today
author: Fionn Smith, Ella Hächler, Linus Folini
bibliography: waste-pickers.bib
format: revealjs
execute:
  warning: false
editor: visual
---

## Research Question

Formalization of Informal Waste Pickers’ Cooperatives in Blantyre, Malawi: A Feasibility Assessment\
@kasinja2018formalization\
<br> How can the formalization of informal waste pickers (IWP) into cooperatives influence the effectiveness and acceptance of municipal solid waste management strategies in unplanned urban settlements in Malawi?

```{r}

```

## Sampling Strategy

-   Interviews

    -   On-site of active IWPs collecting in Zingwangwa (34/42)

    -   Middlemen (2)

    -   Official from Blantyre City Council responsible for MSWM (1)

-   Structured questionnaire

-   Snowball strategy till saturation

-   Cross-sectional study

```{r}

```

## Key Findings

How can the formalization of informal waste pickers into cooperatives influence the effectiveness and accepptance of municipal solid waste management strategies in unplanned urban settlements in Malawi?<br>

-   Storage capacity

-   Increased bargaining power

-   Public trust

```{r}

```

## Sources

```{r}

```
