---
title: "Waste Pickers"
subtitle: "md-08-am-01"
date: today
author: Fionn Smith, Ella Hächler, Linus Folini
bibliography: waste-pickers.bib
format: revealjs
execute:
  warning: false
editor: visual
---

## Research Question

Formalization of Informal Waste Pickers’ Cooperatives in Blantyre, Malawi: A Feasibility Assessment\
@kasinja2018formalization\
<br> How can the formalization of informal waste pickers into cooperatives influence the effectiveness and accepptance of municipal solid waste management strategies in unplanned urban settlements in Malawi?

```{r}

```

## Sampling Strategy

-   Interviews

    -   on-site of active IWP collecting in Zingwangwa, Malawi

    -   in the city with two middlemen

    -   one city council responsible for the MSWM

-   Snowball strategy till saturation

-   Structured questionnaire

```{r}

```

## Key Findings

How can the formalization of informal waste pickers into cooperatives influence the effectiveness and accepptance of municipal solid waste management strategies in unplanned urban settlements in Malawi?<br>

\
With the right support it could potentially be effective at increasing bargaining power of IWPs, thus having the potential to limit exploitative pricing from buyers.

```{r}

```

## Sources

```{r}

```
